О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
Rewrite the definition of characteristic

\begin{definition}
	\cite{kurz2005characteristic}
	A \textit{characteristic} of an integral point set $M$ is such a squarefree number $q$,
	that for any points $M_1, M_2, M_3 \in M$ the area of triangle $M_1 M_2 M_3$
	is $p\sqrt{q}$, where $p$ is rational.
\end{definition}
For given integral point set, the characteristic is determined uniquely.

>>>>

\begin{definition}
	\cite{kurz2005characteristic}
	Let $M$ be a planar integral point set.
	A squarefree number $q$ is called the \textit{characteristic} of $M$,
	if for any points $M_1, M_2, M_3 \in M$ the area of triangle $M_1 M_2 M_3$
	is $p_{1,2,3}\sqrt{q}$ for some rational $p_{1,2,3}$.
\end{definition}
For given integral point set, the characteristic is determined uniquely.
